Just Take the Bus: Analysis of Toronto Bike Theft from 2022-2024

### 2024-11-10 Paper/Article.Rmd
fix typo

---
title: "Just Take the Bus: Analysis of Toronto Bike Theft from 2022-2024"
subtitle: idk 
author:
- Rayan Awad Alim
- Samreen Gill
date: "November 4th 2024"
output: pdf_document
date-format: long
abstract: "This analysis examines Bike theft data obtained from the Tronrot Police Data Portal."

>>>>

---
title: "Just Take the Bus: Analysis of Toronto Bike Theft from 2022-2024"
subtitle: idk 
author:
- Rayan Awad Alim
- Samreen Gill
date: "November 4th 2024"
output: pdf_document
date-format: long
abstract: "This analysis examines Bike theft data obtained from the Toronto Police Data Portal."
